Automated Formal Synthesis\\ of Safe Digital Controllers for Continuous Plants

### 2019-01-21 automatica/paper.tex
ref

A key contribution of this work is that, when synthesizing controllers, it precisely models the finite-precision arithmetic in the digital controller, guaranteeing that these controllers implemented with finite-precision arithmetic are safe. 
Finite-precision arithmetic introduces errors, as shown in Figure~\ref{fig:digitalsystem}. 
Details of how we model this arithmetic are in Section~\ref{sec:} \note{fix?}. 
These errors are present in the real world, and we must model them accurately in order to capture the full behaviour of the model:

@@

The representations used in the plant model and its arithmetic operations are also carried out at a finite precision, 
thus we must account for the corresponding errors.  
\note{rephrase next:} Specifically, our model of the plant variables $x(t)$ and $u(t)$, which are, in reality, continuous quantities, with finite precision in our model. 
We guarantee that the precision we use to represent the plant variables is at least as precise as the precision used in the digital controller and we use interval arithmetic to bound the errors, as detailed in Section~\ref{sec:} \note{fix?}.

>>>>

A key contribution of this work is that, when synthesizing controllers, it precisely models the finite-precision arithmetic in the digital controller, guaranteeing that these controllers implemented with finite-precision arithmetic are safe. 
Finite-precision arithmetic introduces errors, as shown in Figure~\ref{fig:digitalsystem}. 
Details of how we model this arithmetic are in Section~\ref{sec:numeric_rep}. 
These errors are present in the real world, and we must model them accurately in order to capture the full behaviour of the model:

@@

The representations used in the plant model and its arithmetic operations are also carried out at a finite precision, 
thus we must account for the corresponding errors.  
\note{rephrase next:} Specifically, our model of the plant variables $x(t)$ and $u(t)$, which are, in reality, continuous quantities, with finite precision in our model. 
We guarantee that the precision we use to represent the plant variables is at least as precise as the precision used in the digital controller and we use interval arithmetic to bound the errors, as detailed in Section~\ref{sec:numeric_rep}.
